Competition

### 2021-01-06 analysis/wrangling/competition wrangling.Rmd
reorganized files to make R CMD check happier
calculate percentage of plants in database with coordinates

source(here("R", "utils.R"))

@@

>>>>

library(HeliconiaDemography) #load functions in this compendium

@@

What percentage of plants have coordinates?

```{r}
full_join(ha %>% select(-x_09, -y_09),
          ha_coords,
          by = c("plot", "row", "column", "tag_number", "year")) %>% 
  group_by(ha_id_number) %>% 
  summarize(has_coord = any(!is.na(x))) %>%  #true if there is a non-NA value for at least one year
  summarize(percent_with_coords = sum(has_coord)/n())
```
